---
author: "John Flournoy"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
params:
  ROI: 410
  SUBSAMP: FALSE
---

```{css, echo=FALSE}
@import url('https://fonts.googleapis.com/css?family=Didact+Gothic&display=swap');
@import url('https://fonts.googleapis.com/css?family=Fira+Code&display=swap');
body{
  font-family: 'Didact Gothic',  sans-serif;
}
pre code {
  font-family: 'Fira Code',  monospace;
}
```


```{r}
library(data.table)
library(brms)
library(ggplot2)
library(argparse)
library(e1071)
library(patchwork)
library(showtext)
#{.tabset}

font_add_google("Didact Gothic", "Didact Gothic")

knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
#https://www.instagram.com/p/CC3EvmLgt2m/?utm_source=ig_web_copy_link
apal <- paste0('#',c('2C2B2B', 'F9773B', 'FFEA8C', '1389E6', 'D2E5E7'))
jftheme <- theme_minimal() +  
    theme(text = element_text(family = 'Didact Gothic', size = 14),
          panel.background = element_rect(fill = apal[[5]], size = 0, color = apal[[2]]),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(), 
          strip.background = element_rect(fill = apal[[3]], size = 0),
          strip.text = element_text(color = '#222222'),
          axis.text =  element_text(color = apal[[1]]), axis.title = element_text(color = apal[[1]]))


# stat: skew 
skew <- function(x) {
  xdev <- x - mean(x)
  n <- length(x)
  r <- sum(xdev^3) / sum(xdev^2)^1.5
  return(r * sqrt(n) * (1 - 1/n)^1.5)
}

if(params$SUBSAMP){
  suffix <- '-sub'  
} else {
  suffix <- ''
}

task_id <- as.numeric(Sys.getenv('SLURM_ARRAY_TASK_ID'))
cpus_total <- as.numeric(Sys.getenv('SLURM_CPUS_PER_TASK'))

if(is.na(task_id)){
  this_ROI <- params$ROI #TO BE SET BY SLURM ENV VAR
  cpus_total <- 10
  message('Not running as slurm array, setting ROI to some value: ', this_ROI)
} else {
  this_ROI <- task_id
  message('Running as slurm array with task id=ROI: ', task_id, '=', this_ROI)
}
setDTthreads(cpus_total)
```

---
title: "SEA tfMRI - Within-person, Internal Consistency: Parcel `r this_ROI`"
---


>Nezlek, J. B. (2017). A practical guide to understanding reliability in
studies of within-person variability. Journal of Research in Personality, 69,
149–155. https://doi.org/10.1016/j.jrp.2016.06.020


$$
\begin{aligned}
\text{Voxels: } y_{ijk} &= \pi_{0jk} + \epsilon_{ijk}\\
\text{Occasions: } \pi_{0jk} &= \beta_{00k} + \rho_{0jk}\\
\text{Persons: } \beta_{00k} &= \gamma_{000} + \nu_{00k}\\
\\
\text{Combined: } y_{ijk} &= \gamma_{000} + \nu_{00k} + \rho_{0jk} + \epsilon_{ijk}\\
\end{aligned}
$$

Voxel-level reliability for a parcel:

$$
\alpha = \frac{\tau_\pi}{\tau_\pi + \frac{\sigma^2}{j}}
$$

where $\tau_\pi$ indicates the variance of the random component of the
parameter $\pi$, $\sigma^2$ is the variance of the error term
$\epsilon_{ijk}$, and $j$ is the number of voxels.

Important caveat:

>Perhaps more important, similar to the assumptions made when using
Cronbach’s alpha, the items are assumed to be parallel. According to Shrout
and Lane (2012) this means that “(a) Items must be replicate indicators of
the same underlying latent trait, (b) responses to the items must be
independent after adjusting for the level of the latent trait, and (c) the
magnitude of error associated with each item must be the same.”

In addition, the consistency among voxels within a parcel will be elevated by smoothing. That's precisely the reason for doing smoothing in the first place: to average out, over space, residual error.

```{r}
message(params$ROI)
message(params$SUBSAMP)
file_search_regex <- paste0('alpha-fearGTcalm-ROI0*', this_ROI, '(-more_\\d{2})*', suffix, '.rds')
message(file_search_regex)

roi_fits <- dir('fits', pattern = file_search_regex, full.names = TRUE)
message('Found: ', roi_fits)
fits <- lapply(roi_fits, readRDS)

cfit <- brms::combine_models(mlist = fits)
```

# Model summary {.tabset}

## Posterior summary

```{r warning = TRUE}
summary(cfit)
```

## Prior summary

```{r}
prior_summary(cfit)
```

# Model diagnostics {.tabset}

```{r}
np <- nuts_params(cfit)
```

Divergent transitions: `r sum(np$Value[np$Parameter == 'divergent__'])`

## N~~eff~~ ratio

```{r}
bayesplot::mcmc_neff(brms::neff_ratio(cfit, pars = c('sd_id__Intercept', 
                                                     'sd_id:sess__Intercept', 
                                                     'b_Intercept', 'sigma'))) + 
  jftheme
brms::neff_ratio(cfit, pars = c('sd_id__Intercept', 
                                'sd_id:sess__Intercept', 
                                'b_Intercept'))
```

## Autocorrelation within-chain

```{r}
bayesplot::mcmc_acf(cfit, lags = 50, pars = c('sd_id__Intercept', 
                                              'sd_id:sess__Intercept', 
                                              'b_Intercept', 'sigma')) + 
  jftheme

```


## r-hat

```{r}
bayesplot::mcmc_rhat(brms::rhat(cfit))
```

## Trace plot

```{r}
bayesplot::mcmc_trace(cfit, pars = c('sd_id__Intercept', 
                                     'sd_id:sess__Intercept', 
                                     'b_Intercept')) + 
  jftheme
```

## Posterior predictive checks {.tabset}

### Density

```{r}
brms::pp_check(cfit, type = 'dens_overlay')
```

### ECDF

```{r}
brms::pp_check(cfit, type = 'ecdf_overlay')
```

### Skew

```{r}
brms::pp_check(cfit, nsamples = 1000, type = 'stat', stat = 'skew') 
```

### Kurtosis

```{r}
brms::pp_check(cfit, nsamples = 1000, type = 'stat', stat = 'kurtosis')
```

## Divergence Diagnostics {.tabset}

```{r}
fit_array <- as.array(cfit)
bayesplot::color_scheme_set("darkgray")
```

### Parcoord

```{r}
bayesplot::mcmc_parcoord(fit_array, np = np, pars = c('sd_id__Intercept', 
                                                      'sd_id:sess__Intercept', 
                                                      'b_Intercept'),
                         np_style = bayesplot::parcoord_style_np(div_color = "red", div_size = .5, div_alpha = 1))
```

### Pairs plots

```{r}
bayesplot::mcmc_pairs(fit_array, np = np, pars = c('sd_id__Intercept', 
                                                   'sd_id:sess__Intercept', 
                                                   'b_Intercept'),
                      off_diag_fun = c("hex"),
                      # off_diag_args = list(size = 0.75),
                      condition = bayesplot::pairs_condition(),
                      # transform = list('sd_id__Intercept' = 'log',
                      #                  'sd_id:sess__Intercept' = 'log'),
                      np_style = bayesplot::pairs_style_np(div_size = 4))
```

### Chains

```{r}
window <- range(which(np$Value[np$Parameter == 'divergent__'] == 1) %% 4000)
if(window[[1]] == Inf){
  cat('No divergences')
} else {
  bayesplot::mcmc_trace(fit_array, pars = "sd_id__Intercept", np = np, window = window) +
    xlab("Post-warmup iteration")
  bayesplot::mcmc_trace(fit_array, pars = "sd_id:sess__Intercept", np = np, window = window) +
    xlab("Post-warmup iteration")
  bayesplot::mcmc_trace(fit_array, pars = "b_Intercept", np = np, window = window) +
    xlab("Post-warmup iteration") 
}
```

### Log-posterior

```{r}
lp <- log_posterior(cfit)
bayesplot::mcmc_nuts_divergence(np, lp)
```

# Parameters of interest

## Variance parameters

```{r}
bayesplot::mcmc_areas_ridges(fit_array, pars = c('sd_id__Intercept', 
                                                 'sd_id:sess__Intercept'), prob = .95, prob_outer = .99) +
bayesplot::mcmc_areas(fit_array, pars = c('sigma'), prob = .95, prob_outer = .99)
```

## Internal consistency {.tabset}

### Posterior Summary

```{r}
vc <- VarCorr(cfit, summary = FALSE)
# alpha_model_fit
tau_pi <- vc$`id:sess`$sd^2
tau_beta <- vc$id$sd^2
sigma2 <- vc$residual__$sd^2
nvoxel <- length(cfit$data$y)/dim(unique(cfit$data[, c('sess', 'id:sess')]))[[1]]
alpha_post <- tau_pi / (tau_pi + sigma2/nvoxel)
pvar <- tau_pi / (tau_pi + tau_beta + sigma2)
post_df <- data.frame(alpha = alpha_post[,1], prop_var = pvar[,1])

knitr::kable(posterior_summary(post_df, robust = TRUE), digits = 3)
```

### Posterior plot

```{r}
bayesplot::mcmc_areas(post_df, pars = 'alpha', prob = .95, prob_outer = .99, point_est = 'median') + 
  bayesplot::mcmc_areas(post_df, pars = 'prop_var', prob = .95, prob_outer = .99, point_est = 'median')
```

### `lme4` version

```{r}
library(lme4)
#alpha_model_form <- bf(y ~ 1 + (1 | id/sess))

fit <- lmer(y ~ 1 + (1 | id/sess), data = cfit$data)
summary(fit)
vc <- VarCorr(fit)
tau_pi <- diag(vc$`sess:id`)[[1]]
sigma2 <- attr(vc, 'sc')^2
nvoxel <- length(cfit$data[cfit$data$id == 1001 & cfit$data$sess == 01,])
sprintf('Alpha: %0.3f', alpha_est <- tau_pi / (tau_pi + sigma2/nvoxel))
sprintf('Prop var: %0.3f', pvar <- tau_pi / (sum(unlist(lapply(vc, diag))) + sigma2))
```
